libcxx

### 2016-11-30 other/libcxx-slides.tex
cgo

\def \GVN {GVN}

@@

\frame{\frametitle{libcxx-performance improvements}
  \begin{itemize}
  \item PR21192 - Reading from stdin is 1-2 orders of magnitude slower than using libstdc++
    - implementation of sync\_with\_stdio doesn't disable synchronization \url{http://stackoverflow.com/q/33837349}

@@

  \item clang+libc++ vs. gcc+libstdc++ performance update. Constructor of vector in libstdc++ contains memcpy
    in the final assembly.

@@

  \item Removing Heap usage

  \item Missing features (and performance issues) in <regex>

  \item Non-conforming allocators in the test suite

@@

  \item Debug mode for the library
  \end{itemize}
}

>>>>

@@

\frame{\frametitle{libcxx-performance analysis}
  \begin{itemize}
  \item Improving standard library algorithms like string::find, basic_streambuf::xsgetn
  \item inlining the constructor and destructor of std::string
  \item systematic analysis of attributes in the standard library
  \item comparative analysis of clang-libc++ vs. gcc-libstdc++ on representative benchmarks.
  \item clang+libc++ vs. gcc+libstdc++ performance update. Constructor of vector in libstdc++ contains memcpy
    in the final assembly.
  \end{itemize}

  \begin{itemize}
  \item PR21192 - Reading from stdin is 1-2 orders of magnitude slower than using libstdc++
    - implementation of sync\_with\_stdio doesn't disable synchronization \url{http://stackoverflow.com/q/33837349}

@@

@@

@@

  \end{itemize}
}
